Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-30 inst/paper/main.tex
Add two examples of eval

>>>>

Recording calls - this one is more on the misuse than doing something useful. I
really wonder why they do not use \c{do.call(write.table, Call)} (except that it
will create additional frames).
\begin{lstlisting}
write.csv <- function (...)
{
  Call <- match.call(expand.dots = TRUE)
  for (argname in c("append", "col.names", "sep", "dec", "qmethod"))
    if (!is.null(Call[[argname]]))
      warning(gettextf("attempt to set '%s' ignored", argname), domain = NA)
  rn <- eval.parent(Call$row.names)
  Call$append <- NULL
  Call$col.names <- if (is.logical(rn) && !rn) TRUE else NA
  Call$sep <- ","
  Call$dec <- "."
  Call$qmethod <- "double"
  Call[[1L]] <- as.name("write.table")
  eval.parent(Call)
}
\end{lstlisting}

creating and evaling strings - here they assemble the call to plot function. plot is s3 generic which takes
ridiculous amount of parameters and in addition their plot function also takes parameters.
This code could be nicely refactored using do.call.
\begin{lstlisting}
wsbackfit::plot.sback <- function(x, composed = TRUE, ask = TRUE, select = NULL, ...) {
 dots <- list(...)
 grph.opt <- names(dots)
...
 stub <- paste(
  ifelse("xlab" %in% grph.opt, "", paste(", xlab = \"", var, "\"",sep = "")),
  ifelse("ylab" %in% grph.opt, "", paste(", ylab = \"", p.functions[i], "\"", sep = "")),
  ifelse("main" %in% grph.opt, "", main.aux),
  ifelse("type" %in% grph.opt, "", ", type = \"l\""),
  ifelse("ylim" %in% grph.opt, "", paste(", ylim = c(", min.ylim,",", max.ylim,")", sep = "")), ",...)",
  sep = ""
 )

  if(composed) {
          plot <- paste("plot(x.data, y.composed", stub, sep = "")
          eval(parse(text = plot))
          rug(x$data[,var])
  } else {
          plot <- paste("plot(x.data, y.data.nl", stub, sep = "")
          eval(parse(text = plot))

          stub <- paste(ifelse("lty" %in% grph.opt, "", ",lty = 2"), ",...)", sep = "")
          lines <- paste("lines(x.data, y.data.l", stub, sep = "")
          eval(parse(text = lines))

          rug(x$data[,var])
          stub <- paste(ifelse("lty" %in% grph.opt, "", "lty = 1:2"), ", legend = c(\"Non linear\",\"Linear\"), bty = \"n\"", ", cex = ", dots$cex,")", sep = "")
          legend <- paste("legend(\"topleft\",", stub, sep = "")
          eval(parse(text = legend))
  }
...
}
\end{lstlisting}
